A Data-Driven Framework for Neural Field Modeling

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
applied ken comments
minor edits

The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function 
\begin{equation}
	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{1}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
\end{equation}
The parameter $v_0$ describes the firing threshold of the neural populations and $\varsigma$ governs the slope of the sigmoid. By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model 
\begin{equation}
	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
	\int_{-\infty}^t 
	h\left(t - t'\right) \int_\Omega
	w\left(\mathbf{r},\mathbf{r}'\right) 
	f\left( v\left( \mathbf{r}',t' \right)\right)
	\, d\mathbf{r}'dt'.
\end{equation}
\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the differential operator $\textrm{D}=d/dt + \zeta$. A Green's function satisfies
\begin{equation}
	\label{GreensFuncDef} \textrm{D}h\left( t \right) = \delta \left( t \right), 
\end{equation} 
where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ to equation~\ref{FullDoubleIntModel} gives
\begin{align}
 \textrm{D}v\left(\mathbf r,t\right)&= \textrm{D}\left(h\ast g\right)\left(\mathbf r,t\right)\\
&=\left(\textrm{D}h\ast g\right)\left(\mathbf r,t\right)\\
&=\left(\delta \left(t\right)\ast g\right)\left(\mathbf r,t\right)\\
&=g\left(\mathbf r,t\right)
\end{align}
where $\ast$ denotes the convolution operator.} This gives the standard form of the model
\begin{equation}
	\label{FinalFormContinuous} 
	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
\end{equation}
To arrive at the integro-difference equation (IDE) form of the model, we discretize time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
\begin{equation}
	\label{DiscreteTimeModel} 
	v_{t+T_s}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r}'\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, d\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$ (\cite{Rasmussen2005}). The disturbance is added to account for model uncertainty and unmodeled inputs. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.

@@

The connectivity kernel can also be decomposed as 
\begin{equation}\label{DefKernelDecomp}
	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
\end{equation}
where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. \dean{A graphical demonstration of the connectivity kernel decomposition is provided in Figure~\ref{fig:Figure1}.} By exploiting the isotropy of the connectivity basis functions, they can be written as  
$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$. The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented. Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.}

@@

\subsection{Estimation of Connectivity Kernel Support}
\dean{The support of the connectivity kernel can be inferred using spatial correlation analysis. The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}. To demonstrate the method for the neural field model we assume the sensors are infinitesimally close (continuous observation). The spatial cross-correlation function between consecutive observations is defined as 
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \\
	&= \mathbf{E}\left[\left(m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) + \boldsymbol{\varepsilon}_t\left(\mathbf{r}\right) \right) \times \left( m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) + \boldsymbol{\varepsilon}_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right], \label{eq:ObsXCorr}
\end{align}
where $\mathbf{E}[\cdot]$ is the expected value. Since the observation noise is temporally white and independent of the field, equation~\ref{eq:ObsXCorr} reduces to
\begin{equation}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_{t+1}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right].
\end{equation}
Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left( \xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) + e_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \\	
	 &= \xi \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right] \nonumber \\
	&+ T_s\mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right] \nonumber \\
	&+ \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast e_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]
	\\
	&= R_1(\boldsymbol{\tau}) + R_2(\boldsymbol{\tau}) + R_3(\boldsymbol{\tau}).\label{eq:spatialxcorr} 
\end{align}
The last term on the right hand side of equation~\ref{eq:spatialxcorr} is
\begin{equation}
	R_3(\boldsymbol{\tau}) = 0,
\end{equation}
since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$. Putting to other two terms back together we can write
\begin{equation}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) = \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast f\left(v_t\left(\mathbf{r}+\boldsymbol{\tau}\right)\right) \right) \right]
\end{equation}
Now we assume that sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
\begin{equation}
	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
		0, & v_t(\mathbf{r}') \le v_1 \\
		\varsigma v_t(\mathbf{r}'), &  v_1 < v_t(\mathbf{r}') < v_2 \\
		1, & v_t(\mathbf{r}') \ge v_2 \\ 
		\end{array}\right.
\end{equation}
Furthermore, we assume the field is in the linear region of the piecewise function for the majority of the time. 
\begin{equation}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \mathbf{E}\left[ m\left(\mathbf{r}\right) \ast v_t\left(\mathbf{r}\right) \times m\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \left(\xi v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) + T_s w\left(\mathbf{r}+\boldsymbol{\tau}\right) \ast \varsigma v_t\left(\mathbf{r}+\boldsymbol{\tau}\right) \right) \right]
\end{equation}
Now we take the Fourier transform of the terms inside the expectation giving
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &\approx \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu})V(\boldsymbol{\nu}) \ast \left(\xi e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} V(\boldsymbol{\nu}) + T_s e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} \varsigma V(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast \left(\xi e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) + T_s e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) \varsigma V(\boldsymbol{\nu}) e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[\mathcal{F}^{-1} \left\{M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \ast e^{2i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} M(\boldsymbol{\nu}) V(\boldsymbol{\nu}) \left(\xi + T_s \varsigma e^{i\boldsymbol{\nu}^{\top}\boldsymbol{\tau}} W(\boldsymbol{\nu}) \right) \right\} \right] \\
	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \ast \left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \\
	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau}) \right] \ast \mathbf{E}\left[\left( \xi\delta_D(\mathbf{r}) + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right) \right] \label{eq:xcorr_pre_sub}
\end{align}
where $\mathcal{F}^{-1}$ denotes the inverse Fourier transform and $R_{y_{t},y_{t}}(\boldsymbol{\tau})$ is the auto-correlation of the observations, $\delta_K(\cdot)$ is the Kronecker delta function, and $\delta_D(\cdot)$ is the Dirac delta function. We define the auto-correlation of the observations as
\begin{align}
	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[ y_{t}\left(\mathbf{r}\right) y_{t}\left(\mathbf{r}+\boldsymbol{\tau}\right) \right]\\
	&= \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right] + \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2
\end{align}
Rearrange to get
\begin{equation}\label{eq:autocorr_for_sub}
	R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta_K(\boldsymbol{\tau})\sigma_{\varepsilon}^2 = \mathbf{E}\left[m(\mathbf{r}) \ast v_t(\mathbf{r}) \times m(\mathbf{r}+\boldsymbol{\tau}) \ast v_t(\mathbf{r}+\boldsymbol{\tau})\right].
\end{equation}
Now to isolate the kernel equation~\ref{eq:autocorr_for_sub} is substituted into equation~\ref{eq:xcorr_pre_sub} and the Fourier transform is taken giving
\begin{align}
	\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\} &\approx \mathcal{F}\left\{ \left(R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2\right) \ast \mathbf{E} \left[ \xi\delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right] \right\} \\
	&= \mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right) \sigma_{\varepsilon}^2 \right\} \mathcal{F}\left\{\mathbf{E}[ \xi \delta_D(\mathbf{r})  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) ]\right\}.
\end{align}
Now rearranging
\begin{equation}
	\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}} \approx \mathcal{F}\left\{ \mathbf{E}\left[ \xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau}) \right]\right\}.
\end{equation}
Take inverse Fourier transform and rearrange to get an approximation of the kernel
\begin{equation}
	\mathcal{F}^{-1}\left\{\frac{\mathcal{F}\left\{R_{y_{t},y_{t+1}}(\boldsymbol{\tau})\right\}}{\mathcal{F}\left\{ R_{y_t,y_t}(\boldsymbol{\tau}) - \delta_K\left(\boldsymbol{\tau}\right)\sigma_{\varepsilon}^2 \right\}}\right\} \approx \mathbf{E}[\xi\delta_D\left(\mathbf{r}\right)  + T_s \varsigma w(\mathbf{r}+\boldsymbol{\tau})].
\end{equation}
This equation states that the support of the kernel can be estimated given knowledge of $\sigma_\varepsilon^2$. Furthermore, is we assume a local coupling (at $\boldsymbol\tau=0$) regime, either excitation or inhibition, than we don't even need to know $\sigma_\varepsilon^2$. The peak in the kernel at $\mathbf{r}=0$ will be bigger or smaller if we guess incorrectly and the kernel parameters can do the rest! }
% 
% \begin{align}
% 	middle term &= T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) f\left(v_t\left(\mathbf{r}''\right)\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \\
% 	&=T_s\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n-\mathbf{r}'\right)\int_\Omega { w\left(\mathbf{r}',\mathbf{r}''\right) \varsigma v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right] \label{eq:preswap}  \\
% 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \int_\Omega {  m\left(\mathbf{r}'-\mathbf{r}''\right) v_t\left(\mathbf{r}''\right)\, d\mathbf{r}''}\, d\mathbf{r}'}\right]  \label{eq:postswap} \\
% 	&= T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\right],	
% \end{align}
% where the associativity and commutativity algebraic properties of the spatial convolution where used to move from equation~\ref{eq:preswap} to equation~\ref{eq:postswap}.
% % 
% % Evaluating the middle term for the saturation regions. If $v_t(\mathbf{r}') \le v_1$ then the middle term will equate to zero. If $v_t(\mathbf{r}') \ge v_2$ then we get
% % \begin{align}
% % 	middle term &= T_s \mathbf{E} \left[ \bar{y}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right) \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}''\right) \, d\mathbf{r}''} \, d\mathbf{r}'} \right] \\
% % 	&= T_s a_1 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}'\right)\, d\mathbf{r}'} \right] \\
% % 	&= T_s a_1 a_2 \mathbf{E}\left[ \bar{y}_t \left( \mathbf{r}_n + \boldsymbol{\tau} \right) \right],
% % \end{align}
% % where $a_1$ is the integral of the connectivity kernel and $a_2$ is the integral of the observation kernel.
% 
% The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
% \begin{equation}
% 	R_1(\boldsymbol{\tau}) = \xi R_{\bar{y}_{t},\bar{y}_{t}}(\boldsymbol{\tau}),
% \end{equation}
% which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$.
% 
% Under the assumption that the field is in the linear region of the sigmoid for the majority of time then
% \begin{equation}\label{eq:approx_xcorr}
% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi R_{  \bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].
% \end{equation}
% The autocorrelation of the noisy observations is
% \begin{equation}\label{eq:autocorrelation_of_y}
% 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) = R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2,
% \end{equation}
% where $\delta(\cdot)$ is the Kronecker delta function. Rearranging equation~\ref{eq:autocorrelation_of_y} and substituting it into equation~\ref{eq:approx_xcorr} gives
% \begin{equation}
% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) \approx \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) + T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right],	
% \end{equation}
% and
% \begin{equation}\label{eq:support_estimator}
% 	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) - \xi (R_{y_{t},y_{t}}(\boldsymbol{\tau}) - \delta(\boldsymbol{\tau}) \sigma_{\varepsilon}^2) \approx T_s\varsigma\mathbf{E}\left[ \bar{y}_t\left( \mathbf{r}_n + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r}_n,\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right].	
% \end{equation}
% The right hand side of equation~\ref{eq:support_estimator} will have the structure of the connectivity kernel. To show this let
% \begin{align}
% 	Z &= \mathcal{F}\left\{\bar{y}_t\left( \mathbf{r} + \boldsymbol{\tau} \right) \int_{\Omega}{ w\left(\mathbf{r},\mathbf{r}'\right) \bar{y}_t\left( \mathbf{r}' \right)\, d\mathbf{r}'}\right\} \\
% 	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})\bar{Y}(\boldsymbol{\nu}) \ast W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \\
% 	&= \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \ast \bar{Y}(\boldsymbol{\nu}),
% \end{align}
% using the associativity with scalar multiplication property of convolution. Now taking the inverse Fourier transform
% \begin{align}
% 	z &= \mathcal{F}^{-1}\left\{ \exp(i\boldsymbol{\nu}^{\top}\boldsymbol{\tau})W(\boldsymbol{\nu})\bar{Y}(\boldsymbol{\nu}) \ast \bar{Y}(\boldsymbol{\nu})\right\} \\
% 	&= w(\mathbf{r}+\boldsymbol{\tau}) \ast \bar{y}^2(\mathbf{r}) \\
% 	&= \int_{\Omega}{w(\mathbf{r}+\boldsymbol{\tau},\mathbf{r}')\bar{y}^2(\mathbf{r}')d\mathbf{r}'}
% \end{align}
% 
% 
% This may hold:
% \begin{equation}
% 	R_{\bar{y}_{t},\bar{y}_{t} } (\boldsymbol{\tau}) = \sigma_d \int_{\Omega}{ m(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}')\int_{\Omega}{ m(\mathbf{r}'_n-\mathbf{r}'') \gamma(\mathbf{r}'-\mathbf{r}'') d\mathbf{r}''} d\mathbf{r}'}.
% \end{equation}
% If it does then we can estimate the support of the disturbance using the correlation analysis if the bandwidth of the sensor is wider than the bandwidth of the disturbance.\\
% the proof of the above\\
% \begin{align}
% 	R_{y_{t},y_{t}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\left(\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t\left(\mathbf{r}_n+\boldsymbol{\tau}\right)\right) \left(\int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''} + \boldsymbol{\varepsilon}_{t}\left(\mathbf{r}_n\right)\right) \right]\\
% 		&=\mathbf{E}\left[\int_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'} \int_{\Omega}{ m\left(\mathbf{r}_n - \mathbf{r}''\right) v_{t}\left(\mathbf{r}''\right) \, d\mathbf{r}''}\right] + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2 \\
% 		&=\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right) \mathbf{E}\left[v_t\left(\mathbf{r}'\right) v_{t}\left(\mathbf{r}''\right)\right]\, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\\
% 		&=\sigma_d\iint_{\Omega}{ m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) m\left(\mathbf{r}_n - \mathbf{r}''\right)\gamma(\mathbf{r}'-\mathbf{r}'') \, d\mathbf{r}'}{ \, d\mathbf{r}''} + \delta(\boldsymbol{\tau})\sigma_{\varepsilon}^2\label{eq:ObsCorr}
% \end{align}

% Therefore we can write
% \begin{equation}
% 	R_{v_{t},v_{t+1}}(\mathbf{\tau}) = \xi R_{v_{t},v_{t}}(\mathbf{\tau}) + T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}\label{eq:xcorr_firing_and_field}
% 	T_s R_{v_{t},g_{t}}(\mathbf{\tau}) = R_{v_{t},v_{t+1}}(\mathbf{\tau})-\xi R_{v_{t},v_{t}}(\mathbf{\tau}).
% \end{equation}
% The spatial cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$ depends on the shape of the spatial mixing kernel $w\left( \mathbf{r},\mathbf{r}' \right)$. Furthermore, the sign (polarity) of $R_{v_{t},g_{t}}(\mathbf{\tau})$ will be the same as the $w\left( \mathbf{r},\mathbf{r}' \right)$ for a given spatial location since the sigmoid function $f\left( v_t\left( \mathbf{r}' \right) \right) > \mathbf{0}$. Therefore, the support of the kernel can be inferred given the cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$. The right hand side of equation~\ref{eq:xcorr_firing_and_field} can be calculated from data if $\xi$ is known. However, since $\xi$ is a decay parameter, we know that $\xi \in (0,1)$. Also, if we assume that
% \begin{equation}
% 	\xi R_{v_{t},v_{t}}(\mathbf{\tau}) \gg T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}
% 	R_{v_{t},g_{t}}(\mathbf{0}) > 0,
% \end{equation}
% which corresponds to local excitation, then we can guess $\xi$ by incrementally increasing it from zero and evaluating equation~\ref{eq:xcorr_firing_and_field} until $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$. The value of $\xi$ before $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$ will provide the approximation.

>>>>

The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function 
\begin{equation}
	\label{ActivationFunction} f\left( v\left( \mathbf{r}', t \right) \right) = \frac{1}{1 + \exp \left( \varsigma \left( v_0 - v\left(\mathbf{r}',t\right) \right) \right)}. 
\end{equation}
The parameter $v_0$ describes the firing threshold of the neural populations and $\varsigma$ governs the slope of the sigmoid. By substituting equation~\ref{RateBasedInteractions} into equation~\ref{SpikesToPotential} we get the spatiotemporal model 
\begin{equation}
	\label{FullDoubleIntModel} v\left(\mathbf{r},t\right) =
	\int_{-\infty}^t 
	h\left(t - t'\right) \int_\Omega
	w\left(\mathbf{r},\mathbf{r}'\right) 
	f\left( v\left( \mathbf{r}',t' \right)\right)
	\, d\mathbf{r}'dt'.
\end{equation}
\dean{(reviewer 2, comment 3:) To arrive at the standard integro-differential equation form of the model, we use the fact that the synaptic response kernel is a Green's function of a linear differential equation defined by the operator $\textrm{D}=d/dt + \zeta$. A Green's function satisfies
\begin{equation}
	\label{GreensFuncDef} \textrm{D}h\left( t \right) = \delta \left( t \right), 
\end{equation} 
where $\delta(t)$ is the Dirac-delta function. Applying the differential operator $\textrm{D}$ to equation~\ref{FullDoubleIntModel} gives
\begin{align}
 \textrm{D}v\left(\mathbf r,t\right)&= \textrm{D}\left(h\ast g\right)\left(\mathbf r,t\right)\\
&=\left(\textrm{D}h\ast g\right)\left(\mathbf r,t\right)\\
&=\left(\delta \left(t\right)\ast g\right)\left(\mathbf r,t\right)\\
&=g\left(\mathbf r,t\right)
\end{align}
where $\ast$ denotes the convolution operator.} This gives the standard form of the model
\begin{equation}
	\label{FinalFormContinuous} 
	\frac{dv\left( \mathbf{r},t \right)}{dt} + \zeta v\left( \mathbf{r},t \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)\, d\mathbf{r}'}. 
\end{equation}
To arrive at the integro-difference equation (IDE) form of the model, we discretize time using a first-order Euler method (see \ref{App:Time Discretization} for derivation) giving 
\begin{equation}
	\label{DiscreteTimeModel} 
	v_{t+T_s}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r}'\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, d\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where $T_s$ is the time step, $\xi = 1-T_s\zeta $ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean Gaussian process with spatial covariance function $\gamma(\mathbf{r}-\mathbf{r}')$ (\cite{Rasmussen2005}). The disturbance is added to account for model uncertainty and unmodeled inputs. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.

@@

The connectivity kernel can also be decomposed as 
\begin{equation}\label{DefKernelDecomp}
	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
\end{equation}
where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. \dean{A graphical demonstration of the connectivity kernel decomposition is provided in Fig.~\ref{fig:Figure1}.} By exploiting the isotropy of the connectivity basis functions, they can be written as  
$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels, provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$. The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented. Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a compact support.}

@@
